\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-24 paper.tex
Appendix D2

However, service providers have to refund credits to users if their bandwidth availability targets according the agreed SLAs are violated (see $\S$\ref{background}), both for users affected \textit{directly} by the failure and for users \textit{collaterally} affected by the recovery procedure. 
Our failure recovery scheme takes this economic factor into account in the way as follows.

\begin{figure}[t]
\centering
\subfigure[Original allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-1.pdf}}
\subfigure[Backup allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-2.pdf}}
%\caption{There are two services from DC1 to DC4 and link capacity is 1 everywhere. (a) shows the original TE allocation. (b) shows the backup allocation result when assuming link DC2 $\to$ DC4 is broken.  }
\caption{Pre-compute Backup allocation for link failure on DC2$\to$DC4}
\label{recovery}
\end{figure}
%\begin{equation}
%\small
%\begin{aligned} \label{BATE-recovery}
% &maximize  \sum_{i\in I_a} \sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}}\\
%&\begin{array}{r@{\quad}r@{}l@{\quad}l}
%s.t.
%\begin{cases}
%\sum_{i\in I_a}\sum_{k\in K}\sum_{t\in Q_{h}} f'_{ikt}u_t^e+ \sum_{i\in I_a}\sum_{k\in K}\sum_{t'\in Q_{h}} f''_{ikt'}L_{t'e} \le c_e, &\text{$\forall e \in E \setminus e' $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K,\forall t\in T_{k}}.\\
%\end{cases}\\
%\end{array}
%\end{aligned}
%\end{equation}

For a given network scenario $ \mathbf{z}$ (where one link failure occurs) in consideration, 
%let
%$f^{\mathbf{z}}_{ikt}$ denote bandwidth of $i$ over tunnel $t\in T^{ \mathbf{z}}_k$, where 
%$T^ { \mathbf{z}}_k$ denote the set of surviving tunnels for the s-d pair $k$ under scenario $ \mathbf{z}$.
the ration of allocated bandwidth to a user's demanded bandwidth is \footnote{This is the same as equation (3), but we omit the superscript $\mathbf{z}$ of $R_{dk}^\mathbf{z}$.}
\begin{small}
\begin{eqnarray} \label{B-return}
R_{dk}}=\frac{\sum_{t\in T_k f^{t}_{d} v_t^{\mathbf{z}}} {\mathbf{b}^k_d}, \quad \forall  d \in \hat{D},  k \in K
\end{eqnarray}
\end{small}

If for every $k$, $R_{dk}$ is larger than its demand (i.e., $R_{dk} \ge 1$), 
then there is no problem since the demanded availability is still satisfied. 
However, if any $R_{dk}$ falls below 1, then the corresponding SLA will be violated. 
For simplicity, here we assume a simple pricing and refunding model, 
where the charge for serving a user demand $d$ is $g_d$, and if the SLA is violated, 
a fraction $\mu_d$ of $g_d$ will be refunded. 
We use $r_d$ denote the profit of demand $d$ with rufunding, such that

@@

\begin{equation*}
r_d=
\begin{cases}
g_d &\text{$\forall k \in K: R_{dk} \ge 1 $}\\
\(1-mu_{d})g_d &\text{Otherwise}
\end{cases}
\label{availability222}
\end{equation*}

We use an auxiliary integer variable $y_d \in \{0, 1\}$ to denote the violation condition, 
where $y_d=1$ means no violation. 
Then the profit $r_d$ can be rewritten as 
\begin{equation}
\label{A-SSS2}
\begin{array}{rclr}
y_d &\in &\{0,1\} &{\forall d \in \hat{D}} \\
r_d & = & g_d \times \Big(y_d+(1-\mu_{d})\times (1-y_d)\Big) &{\forall d \in \hat{D}} \\
R_{dk}& < & M\times y_d+1-y_d &{\forall d \in \hat{D},  k\in K} \\
R_{dk}& \ge &  y_d, &{\forall d \in \hat{D},  k\in K}
\end{array}
\end{equation}
where $M$ is a constant large enough (e.g., at least larger than the upper bound of $R_{dk}$).

@@

Besides, the bandwidth allocation result $f_t^d$ should be nonnegative
and limited by the available network capacity. 
Let $w_e^{ \mathbf{z}}$ denote whether link $e$ is available under scenario $ \mathbf{z}$, 
then we have 
\begin{equation}
f^{t}_{d} \ge 0, \quad\forall d \in \hat{D} ,  k\in K,  t\in T^{\mathbf{z}}_k.
\label{constraint-f3}
\end{equation}
and 
\begin{small}
\begin{eqnarray} \label{B-constraint}
\sum_{d\in \hat{D}}\sum_{k\in K, t\in T^{ \mathbf{z}}_k} f^{t}_{d}u_t^e \le c_e \times w_e^{ \mathbf{z}}, \forall e \in E
\end{eqnarray}
\end{small}

@@

This mixed-integer linear programming  (MILP) problem can be proved to be NP-hard, 
and the proof details can be found in Appendix \ref{appendix1}.
To efficiently solve this problem, we further propose a 2-approximation greedy algorithm.
The key idea is to prioritize demands by the ratio of profit to the allocated bandwidth in a non-decreasing order.
Due to space limitations, the detailed algorithm, as well as the proof on its optimality, 
are put into Appendix \ref{B}}.

@@

%For the second challenge, although the powerful mathematical optimization solver such as Gurobi \cite{gurobi} can derive the solution, it might be too slow to converge before next TE scheduling epoch.
In this case,  we propose a greedy algorithm to attain an approximate solution whose pseudocode is shown in Appendix \ref{B}.
The key idea of the greedy algorithm is to give priority to demands in non-decreasing order by the ratio of profit to its efficient bandwidth demands.
\textit{We also prove the approximation of the greedy algorithm is 2  in Appendix \ref{B}}. 
%The greedy algorithm can solve $\mathsf{BATE}$  problem in  $O(|J||Z||T_k||E|)$ time.
%We further explore the accuracy of greedy algorithm in Section \ref{evaluation}.
\false

@@

We use $g_d$ to present whether the availability target of $d$ can be satisfied:

\begin{equation}
 g_d=
\begin{cases}
1 &\text{$1 >S_d \ge \beta_{d}$}\\
0 &\text{$ \beta_{d} >S_d\ge 0 $}
\end{cases},
\ \ \ \forall  d \in D.
\label{availability4}
\end{equation}

@@

\begin{equation}
\begin{cases}
S_d <  \beta_{d}\times  (1-g_d)+g_d,& \forall d \in D. \\
S_d \ge  \beta_{d} \times g_d,& \forall d \in D. \\
g_d\in\{0,1\},& \forall d \in D. \\
\end{cases}
\label{g-2}
\end{equation}
%\begin{equation}
%\forall  j \in J : g_j=
%\begin{cases}
%1 &\text{$1>S_j \ge \beta_j^1$}\\
%\alpha_j^1 &\text{$\beta_j^1>S_j \ge \beta_j^2$}\\
%... &\text{$...$}\\
%\mu(R_j)  &\text{$\beta_j^u>S_j \ge0$}
%\end{cases}
%\label{availability}
%\end{equation}
%As TABLE \ref{target} shown, $g_j$ can be used to describe the availability targets defined in SLAs. 
%Applications might have diverse availability demands (i.e., $\beta_j$) and the piecewise formulation also considers this by setting different bound for full profit $\alpha$.
%where $M_2$ is  a big integer that is at least larger than the upper-bound of $S_j,\forall j \in J$.
We intend to maximize the total number of accepted demands, i.e., $ \sum_{d\in D} g_d$.
%\begin{eqnarray} \label{goal}
%maximize  \sum_{i\in I} g_i
%\end{eqnarray}
%where $w_j$ presents the importance of service $j$.
%It considers bandwidth-based availability profit and the importance of services simultaneously.
%Note, constraints (\ref{CA}) and  (\ref{availability}) have piecewise functions which are nonlinear.
With the constraints introduced above, we can finally give the formulation of admission problem:

@@

\begin{equation}
\small
\begin{aligned} \label{P8}
 &maximize  \sum_{d\in D} g_d\\
&\begin{array}{r@{\quad}r@{}l@{\quad}l}
s.t.
(\ref{constraint-f}), (\ref{constraint-e}), (\ref{R}), (\ref{A-z2}), (\ref{S}), (\ref{g-2})
%\begin{cases}
% \sum_{d \in D}\ \sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tu_t^e \le c_e, &\text{$\forall e \in E $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in D, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%S_i=\sum_{\mathbf{z}\in \mathbf{z}}A_d^{\mathbf{z}}\times p_{\mathbf{z}} , & {\forall  d \in D.}\\
%R_{dk}^{\mathbf{z}} < 1- A_d^{\mathbf{z}}+M\times A_d^{\mathbf{z}},&{\forall d \in D, \mathbf{z} \in Z, k\in K.} \\
%R_{dk}^{\mathbf{z}}>=A_d^{\mathbf{z}},&{\forall d \in D, \mathbf{z} \in Z, k\in K.} \\
%S_i <  \beta_{\gamma_{i}}\times  (1-g_i)+g_i,& \forall d \in D. \\
%S_i \ge  \beta_{\gamma_{i}} \times g_i,& \forall d \in D. \\
%f_{d}^t \ge 0,&{\forall d \in D , \forall k\in K, \forall t\in T_{k}}.\\
%A_d^{\mathbf{z}}, g_i\in\{0,1\}, & \forall \mathbf{z} \in \mathbf{z}, d \in D. \\
%\end{cases}\\
\end{array}
\end{aligned}
\end{equation}
\section{Proof of Theorem \ref{NP-222}} \label{appendix-proof}

@@

\begin{appendices}
     \section{Greedy algorithm for failure recovery} \label{B}
     \begin{algorithm}
\KwIn{Input parameters shown in Table \ref{Notation}, a failure scenario $\bm{z}$} 
\KwOut{ $\{f^t_{d}\},F$}
Sort $d\in \hat{D}$ in non-decreasing order with $\frac{w_d}{\sum_{k\in K}\mathbf{b}^k_d}$;\\
$h_d=0, \forall d \in \hat{D}$; \\
$F=\{\}$;\\
\For{$d \in \hat{D}$}{
%$\{f'_{ikt}\},h_i,\{D_e\}\leftarrow$Allocation($F,i,B$);\\
%$h_d \leftarrow$ ;\\
\If { $\bm{z}$' s remaining capacity can support $d$}{
$h_d=1$;\\
    $F=F\cup {d}$;\\
    Update $\{f^t_{d}\}$;\\
   Update $\bm{z}$' s remaining network capacity;\\
}
\Else{
\If{$\sum_{d'\in F}w_d' <w_d$}{
\If {Recycling network resource allocated to demands in $F$ is able to support $d$}{
Recycle network resource allocated to demands in $F$;\\
     $F= \{d\}$;\\
    Update $\{f^t_{d}\},\forall d \in \hat{D}$;\\
$\bm{break}$; \\
}
}
\Else{
$\bm{break}$;
}

@@

\begin{proof}
Algorithm \ref{greedy} prefers accepted demands according to the following sequence:
 \begin{eqnarray} \label{B-2}
\frac{w_1}{\sum_{k\in K} d_{1k}} \ge \frac{w_2}{\sum_{k\in K}d_{2k}} \ge ....
\end{eqnarray}

(\ref{B-2})  means the priority of flow pair is decided by the unit value.
W.l.o.g., assume that the network can't transfer the $n+1$ demand,  Algorithm \ref{greedy} will choose $max\{w_{n+1},\sum_{i=1}^{n}w_i\}$ as the value.
Let $OPT$ denote the optimal solution and it is obvious that  $\sum_{i=1}^{n} w_i\le OPT$.
Also, we have  $\sum_{i=1}^{n+1} w_i\ge OPT$.
This holds, since we've already made the density of network as high as possible by the greedy method.
If we violate the link capacity constraint and put the $n+1$ demand into the link, then the link is fulfilled.
There is no other way that the density of the link is greater than this, that is, the value is greater than $OPT$. 
 $\sum_{i=1}^{n+1} w_i/2 \le max\{\sum_{i=1}^{n} w_i,w_{n+1}\}$.
 Therefore, $OPT/2 \le max\{\sum_{i=1}^{n} w_i,w_{n+1}\}$. This completes the
proof.
\end{proof}

>>>>

However, service providers have to refund credits to users if their bandwidth availability targets according the agreed SLAs are violated (see $\S$\ref{background}), both for users affected \textit{directly} by the failure and for users \textit{collaterally} affected by the recovery procedure. 
Our failure recovery scheme takes this economic factor into account in the way as follows.
%
%
%
\begin{figure}[t]
\centering
\subfigure[Original allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-1.pdf}}
\subfigure[Backup allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-2.pdf}}
%\caption{There are two services from DC1 to DC4 and link capacity is 1 everywhere. (a) shows the original TE allocation. (b) shows the backup allocation result when assuming link DC2 $\to$ DC4 is broken.  }
\caption{Pre-compute Backup allocation for link failure on DC2$\to$DC4}
\label{recovery}
\end{figure}
%\begin{equation}
%\small
%\begin{aligned} \label{BATE-recovery}
% &maximize  \sum_{i\in I_a} \sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}}\\
%&\begin{array}{r@{\quad}r@{}l@{\quad}l}
%s.t.
%\begin{cases}
%\sum_{i\in I_a}\sum_{k\in K}\sum_{t\in Q_{h}} f'_{ikt}u_t^e+ \sum_{i\in I_a}\sum_{k\in K}\sum_{t'\in Q_{h}} f''_{ikt'}L_{t'e} \le c_e, &\text{$\forall e \in E \setminus e' $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K,\forall t\in T_{k}}.\\
%\end{cases}\\
%\end{array}
%\end{aligned}
%\end{equation}

For a given network scenario $ \mathbf{z}$ (where one link failure occurs) in consideration, 
%let
%$f^{\mathbf{z}}_{ikt}$ denote bandwidth of $i$ over tunnel $t\in T^{ \mathbf{z}}_k$, where 
%$T^ { \mathbf{z}}_k$ denote the set of surviving tunnels for the s-d pair $k$ under scenario $ \mathbf{z}$.
the ration of allocated bandwidth to a user's demanded bandwidth is \footnote{This is the same as equation (3), but we omit the superscript $\mathbf{z}$ of $R_{dk}^\mathbf{z}$.}

\begin{small}
\begin{eqnarray} \label{B-return}
R_{dk}=\frac{\sum_{t\in T_k} f^{t}_{d} v_t^{\mathbf{z}}} {\mathbf{b}^k_d}, \quad \forall  d \in \hat{D},  k \in K
\end{eqnarray}
\end{small}

If for every $k$, $R_{dk}$ is larger than its demand (i.e., $R_{dk} \ge 1$), 
then there is no problem since the demanded availability is still satisfied. 
However, if any $R_{dk}$ falls below 1, then the corresponding SLA will be violated. 
For simplicity, here we assume a simple pricing and refunding model, 
where the charge for serving a user demand $d$ is $g_d$, and if the SLA is violated, 
a fraction $\mu_d$ of $g_d$ will be refunded. 
We use $r_d$ denote the profit of demand $d$ with refunding, such that

@@

\begin{equation}
r_d=
\begin{cases}
g_d &\text{$\forall k \in K: R_{dk} \ge 1$ }\\
(1-\mu_{d})g_d &\text{Otherwise}
\end{cases}
\label{availability222}
\end{equation}

%\begin{equation}
%A_d^{\mathbf{z}}=
%\begin{cases}
%1 &\text{$\forall k \in K:R_{dk}^{\mathbf{z}}\ge 1$}\\
%0&\text{Otherwise}
%\end{cases}
%,\forall  d \in D, \mathbf{z}\in \mathbf{z}.
%\label{CA}
%\end{equation}

We use an auxiliary integer variable $y_d \in \{0, 1\}$ to denote the violation condition, 
where $y_d=1$ means no violation. 
Then the profit $r_d$ can be rewritten as

\begin{equation}
\label{A-SSS2}
\begin{cases}
y_d \in \{0,1\} &{\forall d \in \hat{D}} \\
r_d  =  g_d \times \Big(y_d+(1-\mu_{d})\times (1-y_d)\Big) &{\forall d \in \hat{D}} \\
R_{dk} <  M\times y_d+1-y_d &{\forall d \in \hat{D},  k\in K} \\
R_{dk} \ge   y_d &{\forall d \in \hat{D},  k\in K}
\end{cases}
\end{equation}

where $M$ is a constant large enough (e.g., at least larger than the upper bound of $R_{dk}$).

@@

Besides, the bandwidth allocation result $f_t^d$ should be nonnegative
and limited by the available network capacity. 
Let $w_e^{ \mathbf{z}}$ denote whether link $e$ is available under scenario $ \mathbf{z}$, 
then we have 
\begin{equation}
f^{t}_{d} \ge 0, \quad\forall d \in \hat{D} ,  k\in K,  t\in T_k.
\label{constraint-f3}
\end{equation}
and 
\begin{small}
\begin{eqnarray} \label{B-constraint}
\sum_{d\in \hat{D}}\sum_{k\in K, t\in T^{ \mathbf{z}}_k} f^{t}_{d}u_t^e \le c_e \times w_e^{ \mathbf{z}}, \forall e \in E
\end{eqnarray}
\end{small}

@@

This mixed-integer linear programming  (MILP) problem can be proved to be NP-hard, 
and the proof details can be found in Appendix \ref{appendix1}.
To efficiently solve this problem, we further propose a 2-approximation greedy algorithm.
The key idea is to prioritize demands by the ratio of profit to the allocated bandwidth in a non-decreasing order.
Due to space limitations, the detailed algorithm, as well as the proof on its optimality, 
are put into Appendix \ref{B}.

@@

%For the second challenge, although the powerful mathematical optimization solver such as Gurobi \cite{gurobi} can derive the solution, it might be too slow to converge before next TE scheduling epoch.
In this case,  we propose a greedy algorithm to attain an approximate solution whose pseudocode is shown in Appendix \ref{B}.
The key idea of the greedy algorithm is to give priority to demands in non-decreasing order by the ratio of profit to its efficient bandwidth demands.
\textit{We also prove the approximation of the greedy algorithm is 2  in Appendix \ref{B}}. 
%The greedy algorithm can solve $\mathsf{BATE}$  problem in  $O(|J||Z||T_k||E|)$ time.
%We further explore the accuracy of greedy algorithm in Section \ref{evaluation}.
\fi

@@

We use $y_d$ to present whether the availability target of $d$ can be satisfied:

\begin{equation}
 y_d=
\begin{cases}
1 &\text{$1 >S_d \ge \beta_{d}$}\\
0 &\text{$ \beta_{d} >S_d\ge 0 $}
\end{cases},
\ \ \ \forall  d \in D.
\label{availability4}
\end{equation}

@@

\begin{equation}
\begin{cases}
S_d <  \beta_{d}\times  (1-y_d)+y_d,& \forall d \in D. \\
S_d \ge  \beta_{d} \times y_d,& \forall d \in D. \\
y_d\in\{0,1\},& \forall d \in D. \\
\end{cases}
\label{g-2}
\end{equation}
%\begin{equation}
%\forall  j \in J : g_j=
%\begin{cases}
%1 &\text{$1>S_j \ge \beta_j^1$}\\
%\alpha_j^1 &\text{$\beta_j^1>S_j \ge \beta_j^2$}\\
%... &\text{$...$}\\
%\mu(R_j)  &\text{$\beta_j^u>S_j \ge0$}
%\end{cases}
%\label{availability}
%\end{equation}
%As TABLE \ref{target} shown, $g_j$ can be used to describe the availability targets defined in SLAs. 
%Applications might have diverse availability demands (i.e., $\beta_j$) and the piecewise formulation also considers this by setting different bound for full profit $\alpha$.
%where $M_2$ is  a big integer that is at least larger than the upper-bound of $S_j,\forall j \in J$.
We intend to maximize the total number of accepted demands, i.e., $ \sum_{d\in D} y_d$.
%\begin{eqnarray} \label{goal}
%maximize  \sum_{i\in I} g_i
%\end{eqnarray}
%where $w_j$ presents the importance of service $j$.
%It considers bandwidth-based availability profit and the importance of services simultaneously.
%Note, constraints (\ref{CA}) and  (\ref{availability}) have piecewise functions which are nonlinear.
With the constraints introduced above, we can finally give the formulation of admission problem:

@@

\begin{equation}
\small
\begin{aligned} \label{P8}
 &maximize  \sum_{d\in D} y_d\\
&\begin{array}{r@{\quad}r@{}l@{\quad}l}
s.t.
(\ref{constraint-f}), (\ref{constraint-e}), (\ref{R}), (\ref{A-z2}), (\ref{S}), (\ref{g-2})
%\begin{cases}
% \sum_{d \in D}\ \sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tu_t^e \le c_e, &\text{$\forall e \in E $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in D, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%S_i=\sum_{\mathbf{z}\in \mathbf{z}}A_d^{\mathbf{z}}\times p_{\mathbf{z}} , & {\forall  d \in D.}\\
%R_{dk}^{\mathbf{z}} < 1- A_d^{\mathbf{z}}+M\times A_d^{\mathbf{z}},&{\forall d \in D, \mathbf{z} \in Z, k\in K.} \\
%R_{dk}^{\mathbf{z}}>=A_d^{\mathbf{z}},&{\forall d \in D, \mathbf{z} \in Z, k\in K.} \\
%S_i <  \beta_{\gamma_{i}}\times  (1-g_i)+g_i,& \forall d \in D. \\
%S_i \ge  \beta_{\gamma_{i}} \times g_i,& \forall d \in D. \\
%f_{d}^t \ge 0,&{\forall d \in D , \forall k\in K, \forall t\in T_{k}}.\\
%A_d^{\mathbf{z}}, g_i\in\{0,1\}, & \forall \mathbf{z} \in \mathbf{z}, d \in D. \\
%\end{cases}\\
\end{array}
\end{aligned}
\end{equation}
\section{Proof of Theorem \ref{NP-222}} \label{appendix-proof}

@@

\begin{appendices}
     \section{Greedy algorithm for failure recovery} \label{B}
     \begin{algorithm}
\KwIn{Input parameters shown in Table \ref{Notation}, a failure scenario $\bm{z}$} 
\KwOut{ $\{f^t_{d}\},F$}
Sort $d\in \hat{D}$ in non-decreasing order with $\frac{g_d}{\sum_{k\in K}\mathbf{b}^k_d}$;\\
$h_d=0, \forall d \in \hat{D}$; \\
$F=\{\}$;\\
\For{$d \in \hat{D}$}{
%$\{f'_{ikt}\},h_i,\{D_e\}\leftarrow$Allocation($F,i,B$);\\
%$h_d \leftarrow$ ;\\
\If { $\bm{z}$' s remaining capacity can support $d$}{
$h_d=1$;\\
    $F=F\cup {d}$;\\
    Update $\{f^t_{d}\}$;\\
   Update $\bm{z}$' s remaining network capacity;\\
}
\Else{
\If{$\sum_{d'\in F}g_{d'} <g_d$}{
\If {Recycling network resource allocated to demands in $F$ is able to support $d$}{
Recycle network resource allocated to demands in $F$;\\
     $F= \{d\}$;\\
    Update $\{f^t_{d}\},\forall d \in \hat{D}$;\\
$\bm{break}$; \\
}
}
\Else{
$\bm{break}$;
}

@@

\begin{proof}
Algorithm \ref{greedy} prefers accepted demands according to the following sequence:
 \begin{eqnarray} \label{B-2}
\frac{g_1}{\sum_{k\in K}\mathbf{b}^k_1} \ge \frac{g_2}{\sum_{k\in K}\mathbf{b}^k_2} \ge ....
\end{eqnarray}

(\ref{B-2})  means the priority of flow pair is decided by the unit value.
W.l.o.g., assume that the network can't transfer the $n+1$ demand,  Algorithm \ref{greedy} will choose $max\{g_{n+1},\sum_{i=1}^{n}g_i\}$ as the value.
Let $OPT$ denote the optimal solution and it is obvious that  $\sum_{i=1}^{n} g_i\le OPT$.
Also, we have  $\sum_{i=1}^{n+1} g_i\ge OPT$.
This holds, since we've already made the density of network as high as possible by the greedy method.
If we violate the link capacity constraint and put the $n+1$ demand into links, then  links are fulfilled.
There is no other way that the density of links are greater than this, that is, the value is greater than $OPT$. 
 $\sum_{i=1}^{n+1} g_i/2 \le max\{\sum_{i=1}^{n} g_i,g_{n+1}\}$.
 Therefore, $OPT/2 \le max\{\sum_{i=1}^{n} g_i,g_{n+1}\}$. This completes the
proof.
\end{proof}
